### 2022-06-19 latex/Chapters/Chapter0.tex
update

blablabla

>>>>

I am hoping with this project to implement and compare a few different methods to solve the Sliding Puzzle and the Rubik's Cube. Both these games have tremendously large state spaces (see section \hyperref[sec:Games]{Games} for details) and only one goal state. I am therefore likely to only succeed with reasonably small dimensional puzzles, especially since I have chosen for simplicity to implement things in Python.
Depending on the progress I will be able to make in the imparted time, I am hoping to try a mix of simple searches (depth first search, breadth first search, A* with simple admissible heuristics), then more advanced ones such as A* informed by heuristics learnt via DL and DRL. Time permitting I would like to give a go at DQL, and maybe also compare things with some open-source domain-specific implementations (for instance a Kociemba Rubik's algorithm implementation, see e.g. \cite{Kociemba}).
\\
Along the way, I am also hoping to learn a bit about these two games that I have chosen to work on, and maybe make a couple of remarks on them that the reader of this thesis might find interesting.

### 2022-06-19 latex/Chapters/Chapter2.tex
update

\label{Chapter2} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

@@

blablabla

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\section{Rubiks' Cube}

@@

>>>>

\label{sec:Games} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}
%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

@@

The first puzzle I will focus on is the sliding puzzle (see \cite{SlidingPuzzle}).

%-----------------------------------
%	SUBSECTION 1.1
%-----------------------------------
\subsection{Search Space \& Solvability}

@@

%-----------------------------------
%	SUBSECTION 1.2
%-----------------------------------
\subsection{Optimal Cost}

%-----------------------------------
%	SECTION 2
%-----------------------------------
\section{Rubiks' Cube}

### 2022-06-19 latex/MScAIFrancoisBerrier.tex
update

\thesistitle{Solving \\ the \\ Sliding Puzzle \& Rubiks' Cube \\by \\Deep Reinforcement Learning} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Pr. Chris \textsc{Watkins}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{MSc in Artificial Intelligence} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Francois \textsc{Berrier}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

@@

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots
\end{abstract}

@@

\textbf{AIPnT} & \textbf{A}rtificial \textbf{I}ntelligence \textbf{P}rinciples and \textbf{T}echniques\\
\textbf{CS} & \textbf{C}omputer \textbf{S}cience\\
\textbf{CV} & \textbf{C}omputer \textbf{V}ision\\
\textbf{DL} & \textbf{D}eep \textbf{L}earning\\
\textbf{DRL} & \textbf{D}eep \textbf{R}einforcment \textbf{L}earning\\
\textbf{ML} & \textbf{M}achine \textbf{L}earning\\
\textbf{NLP} & \textbf{N}atural \textbf{L}anguage \textbf{P}rocessing\\
\textbf{RC} & \textbf{R}ubiks' \textbf{C}ube\\
\textbf{RL} & \textbf{R}einforcment \textbf{L}earning\\
\textbf{RHUL} & \textbf{R}oyal \textbf{H}olloway, \textbf{U}niversity of \textbf{L}ondon\\
\textbf{SP} & \textbf{S}liding \textbf{P}uzzle\\

>>>>

\thesistitle{Solving \\ the \\ Sliding Puzzle \\ \& \\ Rubiks' Cube \\by \\Deep Reinforcement Learning} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Pr. Chris \textsc{Watkins}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{MSc in Artificial Intelligence} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Francois \textsc{Berrier}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

@@

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
blablabl\ldots
\end{abstract}

@@

\textbf{AIPnT} & \textbf{A}rtificial \textbf{I}ntelligence \textbf{P}rinciples and \textbf{T}echniques\\
\textbf{CS} & \textbf{C}omputer \textbf{S}cience\\
\textbf{CV} & \textbf{C}omputer \textbf{V}ision\\
\textbf{DL} & \textbf{D}eep \textbf{L}earning\\
\textbf{DQL} & \textbf{D}eep \textbf{Q}-\textbf{L}earning\\
\textbf{DRL} & \textbf{D}eep \textbf{R}einforcment \textbf{L}earning\\
\textbf{ML} & \textbf{M}achine \textbf{L}earning\\
\textbf{NLP} & \textbf{N}atural \textbf{L}anguage \textbf{P}rocessing\\
\textbf{RC} & \textbf{R}ubiks' \textbf{C}ube\\
\textbf{RL} & \textbf{R}einforcment \textbf{L}earning\\
\textbf{RHUL} & \textbf{R}oyal \textbf{H}olloway, \textbf{U}niversity of \textbf{L}ondon\\
\textbf{SP} & \textbf{S}liding \textbf{P}uzzle\\
